### 2011-05-10 paper.tex
started the section which proves intersection closure

\section{Essential Properties}

@@

\begin{lemma}\label{ampliftymainlemma}
\begin{enumerate}
\item[] 
\item[(a)] \emph{$\p$} is closed under majority reductions.
\item[(b)] Let $C$ be a \emph{$\{\Sigma,\Pi,\bp,\parity\}$}-constructible complexity class. If $C$ is closed under majority reductions, then (i) \emph{$\Sigma \cdot C$}, (ii) \emph{$\Pi \cdot C$}, (iii) \emph{$\bp \cdot C$}, and (iv) \emph{$\parity \cdot C$} are all closed under majority reductions.
\end{enumerate}
\end{lemma}
\begin{proof}
Part (a) is trivial. For part (b), we consider (i), (ii), (iii), and (iv) separately. Part (iv) is the most difficult, and will not be finished until section \ref{oracle}.
\end{proof}

@@

\begin{theorem}\label{oracle}
Let $C$ be a class containing \emph{$\p$} which is closed under intersection. Then\linebreak \emph{$\parity \cdot (\p^{\parity \cdot C}) = \parity \cdot C$}.
\end{theorem}
\begin{proof}
The direction $\parity \cdot C \subseteq \parity \cdot (\p^{\parity \cdot C})$ is trivial. Let us consider the interesting direction\linebreak $\parity \cdot (\p^{\parity \cdot C})\subseteq \parity\cdot C$.
\end{proof}
\begin{remark}\emph{
While this paper applies Theorem \ref{oracle} only in the case where $C$ is $\{\Sigma,\Pi,\bp,\parity\}$-constructible, it can also be used to show, for instance, that $\parity \cdot (\p^{\parity \cdot \pp}) = \parity \cdot \pp$, although it is nontrivial to show that $\pp$ is closed under intersection. For a proof, see \cite{Beigel}.
}\end{remark}

>>>>

\section{Closed Under Intersection}
%\section{Essential Properties} We should call it this if we have more properties to put here

Consider the following property of a complexity class $C$:
\begin{definition}\label{defintersection}\emph{
We say that a class $C$ is \emph{closed under intersection} if for any languages $L_1,L_2,...,L_k \in C$, the language $\{(x_1,...,x_k) : x_i \in L_i ~ \forall i\}$ is in $C$.
}\end{definition}
It is obvious that a class such as $\p$ is closed under intersection. We will now show that the operators $\Sigma$, $\Pi$, $\bp$, and $\parity$ all preserve this property, which will be important in Section \ref{oracle}
\begin{theorem}\label{theoremintersection}
Let $C$ be a \emph{$\{\Sigma,\Pi,\bp,\parity\}$}-constructible complexity class. Then $C$ is closed under intersection.
\end{theorem}
\begin{proof}

\end{proof}

@@

\begin{lemma}\label{ampliftymainlemma}
\begin{enumerate}
\item[] 
\item[(a)] \emph{$\p$} is closed under majority reductions.
\item[(b)] Let $C$ be a \emph{$\{\Sigma,\Pi,\bp,\parity\}$}-constructible complexity class. If $C$ is closed under majority reductions, then (i) \emph{$\Sigma \cdot C$}, (ii) \emph{$\Pi \cdot C$}, (iii) \emph{$\bp \cdot C$}, and (iv) \emph{$\parity \cdot C$} are all closed under majority reductions.
\end{enumerate}
\end{lemma}
\begin{proof}
Part (a) is trivial. For part (b), we consider (i), (ii), (iii), and (iv) separately. Part (iv) is the most difficult, and will not be finished until Section \ref{oracle}.
\end{proof}

@@

\begin{theorem}\label{oracleparityc}
Let $C$ be a class containing \emph{$\p$} which is closed under intersection. Then\linebreak \emph{$\parity \cdot (\p^{\parity \cdot C}) = \parity \cdot C$}.
\end{theorem}
\begin{proof}
The direction $\parity \cdot C \subseteq \parity \cdot (\p^{\parity \cdot C})$ is trivial. Let us consider the interesting direction\linebreak $\parity \cdot (\p^{\parity \cdot C})\subseteq \parity\cdot C$.
\end{proof}
\begin{remark}\emph{
While this paper applies Theorem \ref{oracle} only in the case where $C$ is $\{\Sigma,\Pi,\bp,\parity\}$-constructible, it can also be used to show, for instance, that $\parity \cdot (\p^{\parity \cdot \pp}) = \parity \cdot \pp$, although it is nontrivial to show that $\pp$ is closed under intersection. For a proof, see \cite{Beigel}.
}\end{remark}
